\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.475in} 
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Marcin Praski} & Email : marcin.praski@live.com \\
  https://github.com/mpraski & Mobile : +48 792 639 099 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University College London}{London, UK}
      {BSc Computer Science, GPA 3.80}{Sep. 2016 -- Jun. 2019}
      \resumeItemListStart
        \resumeItem{Modules include}
          {Logic and Database Theory, Computer Architecture, Concurrency, Compilers, Object-Oriented Programming, Functional Programming, Engineering Mathematics in Finance, Stochastic Calculus and Uncertainty Analysis, Data Mining and Analysis}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Duco}{London, UK}
      {Software Engineer Intern}{Jun. 2018 - Nov. 2018}
      \resumeItemListStart
        \resumeItemPlain
          {Developed dashboard component for specifying regual expressions used to detect certain values in tabular files (Vue, Jest, Ruby on Rails, Rspec).}
        \resumeItemPlain
          {Created Akka actors for search pattern compilation and performing the actual search. Tested and refactored them using JUnit tests (Java, Akka).}
        \resumeItemPlain
          {Developed a third-party integration to allow for workflow collaboration with external customers (Java, Ruby on Rails, Rspec).}
        \resumeItemPlain
          {Participated in development of internal secure file submission tool (React, Enzyme, Rails, Rspec).}
        \resumeItemPlain
          {Aided in identifying and fixing XXE vulnerabilities in XML processor.}
      \resumeItemListEnd

    \resumeSubheading
      {Okinet}{Warsaw, PL}
      {Software Engineering Intern}{Jun. 2016 - Sep. 2016}
      \resumeItemListStart
        \resumeItemPlain
          { Developed backend of a SEO analytics platform dedicated for tracking the position of a domain in Google search engine for given keywords over time. The project involved building a distributed master-slave architecture for periodic polling  of the search engine.}
        \resumeItemPlain
          {Refactored and tested Symfony services using PHPUnit framework.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Clusters}
      {Open source library for cluster analysis in Golang levaraging the language concurrency primitives.}
    \resumeSubItem{PBF Parser}
      {Parser and decoder for OpenStreetMap PBF format written in Elixir.}
    \resumeSubItem{Flow Monitor}
      {Elixir macro for measuring progress of stages in a Flow pipeline.}
    \resumeSubItem{jMonitor}
      {An open source library for monitoring legacy Java programs by injecting chunks bytecode into compiled classes. User can specify targets for monitoring using regular expressions.}
    \resumeSubItem{CPGA}
      {C++ framework for running and testing parallel genetic algorithms executed as actor systems. Developed as part of final year thesis.}
  \resumeSubHeadingListEnd

\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{
      Java, C, C++, Python, Ruby, Erlang
    }
    \resumeSubItem{Frameworks}{
      jUnit, Akka, Boost, Scikit Learn, Ruby on Rails
    }
    \resumeSubItem{Tools}{
      Git, Jira, Eclipse, IntelliJ
    }
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document} 
