\documentclass[a4paper,12pt]{article}

% Adjust hyperrefs
\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\definecolor{dodgerblue}{rgb}{0.12, 0.56, 1.0}
\hypersetup{
  colorlinks=true,
  linkcolor=dodgerblue!50!red,
  urlcolor=dodgerblue!100!black
}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}


% Adjust font
\renewcommand{\familydefault}{\sfdefault}
\usepackage{helvet}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.575in} 
\addtolength{\evensidemargin}{-0.575in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{0pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Marcin Praski} & marcin.praski@live.com \\
  \href{https://mpraski.com}{https://mpraski.com} & +48 792 639 099 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Education \& Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Technische Universität München}{München, DE}
      {MSc Computer Science}{Oct. 2021 -- Now}
    \resumeSubheading
      {Lykon}{Berlin, DE}
      {Software Engineer}{Sep. 2019 - Now}
      \resumeItemListStart
        \resumeItemPlain
          {Build resilient micro-services powering a platform for at-home blood and DNA tests.}
        \resumeItemPlain
          {Provision a container-based infrastructure powered by Kubernetes and AWS using Terraform.}
        \resumeItemPlain
          {Deploy and monitor Kubernetes workloads via Helm.}
        \resumeItemPlain
          {Ensure workload observability via Prometheus, Loki and Grafana.}
      \resumeItemListEnd
    \resumeSubheading
      {Duco}{London, UK}
      {Software Engineer}{Jun. 2018 - Aug. 2019}
      \resumeItemListStart
        \resumeItemPlain
          {Created Akka actors for search pattern compilation and performing the actual search. Tested and refactored them using JUnit tests (Java, Akka).}
        \resumeItemPlain
          {Developed a third-party integration to allow for workflow collaboration with external customers (Java, Ruby on Rails, Rspec).}
        \resumeItemPlain
          {Participated in development of internal secure file submission tool (React, Enzyme, Rails, Rspec).}
      \resumeItemListEnd
    \resumeSubheading
      {University College London}{London, UK}
      {BSc Computer Science, GPA 3.80}{Sep. 2016 -- Jun. 2019}
      \resumeItemListStart
        \resumeItem{Modules}
          {Logic and Database Theory, Computer Architecture, Concurrency, Compilers, Object-Oriented Programming, Functional Programming, Engineering Mathematics in Finance, Stochastic Calculus and Uncertainty Analysis, Data Mining and Analysis}
        \resumeItem{Final year project}
          {\emph{Application of actor model in designing parallel genetic algorithms} - an investigation into how the actor model of computation can be used to implement parallelized genetic algorithms, reference implementation in C++}
      \resumeItemListEnd
    \resumeSubheading
      {IB World School 0704 DP}{Gdynia, PL}
      {IB Diploma Programme, 45/45}{Sep. 2012 -- Jun. 2015}
      \resumeItemListStart
        \resumeItemPlain
          {Higher level subjects: Mathematics, English, History of Europe}
        \resumeItemPlain
          {Standard level subjects: Physics, German, Polish}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Technologies}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{
      Java, C, C++, Golang, Ruby, Elixir
    }
    \resumeSubItem{Frameworks}{
      Kubernetes, Terraform, Helm, Akka, Phoenix
    }
    \resumeSubItem{Services}{
      Git, Jira, AWS, Prometheus, Grafana
    }
  \resumeSubHeadingListEnd


\section{Languages}
  \resumeSubHeadingListStart
    \resumeSubItem{English}{
      Full professional proficiency
    }
    \resumeSubItem{German}{
      Basic professional proficiency
    }
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document} 
